Numerical Stability of Detonations in White Dwarf Simulations

### 2018-11-22 papers/ignition/paper.tex
Update affiliation
Update abstract

\author{Max P. Katz}
\affiliation
{
  NVIDIA Corporation \\
  2788 San Tomas Expressway, Santa Clara, CA, 95051, USA
}
\affiliation
{
  Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY, 11794-3800, USA
}

@@

%==========================================================================
% Abstract
%==========================================================================
\begin{abstract}
Some simulations of Type Ia supernovae feature thermonuclear detonations that
arise naturally during the evolution. It is usually not clear whether these
detonations occur in the same time and place as they would in a simulation
that fully resolved the burning length scale (assuming the resolved simulation
even features a detonation). In this study we explore a number of the algorithmic
choices that affect the outcome of reacting hydrodynamics simulations, and address
the question of what is required to ensure that these simulations are properly
converged. We focus on the spatial and temporal resolution, as well as the coupling
between the hydrodynamics and the reactions. Adaptive mesh refinement, properly
targeted at the relevant burning regions, works well for achieving converged simulations
on a relatively coarse grid.
\end{abstract}
\keywords{supernovae: general - white dwarfs}

>>>>

\author{Max P. Katz}
\affiliation
{
  NVIDIA Corporation, 2788 San Tomas Expressway, Santa Clara, CA, 95051, USA
}

@@

%==========================================================================
% Abstract
%==========================================================================
\begin{abstract}
Some simulations of Type Ia supernovae feature thermonuclear detonations that
arise self-consistently during the evolution. It is not clear whether these
detonations would occur in a simulation that fully resolved the burning. In this
study we examine a test detonation problem inspired by collisions of white dwarfs.
This test problem demonstrates that achieving a converged thermonuclear ignition
requires spatial resolution finer than 1 km in the burning region, and that
the simulation as a whole likely needs a base resolution on the order of 1 km.
Current computational resource constraints place this stringent resolution requirement
out of reach for almost all multi-dimensional supernova simulations.
Consequently, contemporary simulations that self-consistently demonstrate
detonations are very likely not resolved and should not be trusted.
\end{abstract}
\keywords{supernovae: general - white dwarfs}
